What is a Scheme in Algebraic Geometry?

### 2020-11-25 blueprint.tex
Updates blueprint

@@

\begin{definition}[locally ringed space]

@@

\begin{definition}[scheme]

>>>>

\begin{ex}
	Let $X$ be a topological space, $\mathscr{F}$ a sheaf of rings on $X$ and $U$ an open subset of $X$. \\ Prove that $\mathscr{F}|_U$, defined by $\mathscr{F}|_U(V) \coloneqq \mathscr{F}(U \cap V)$, is a sheaf of rings on $U$ for the induced topology.
\end{ex}

@@

\begin{construction}
	Let $X$ be a topological space and $\mathscr{F}$ a sheaf of rings on $X$. The set $I$ will denote a subset of the set of all open subsets of $X$. \\
	Given $U, V \in I$, $s \in \mathscr{F}(U)$ and $t \in \mathscr{F}(V)$,  we says that 
	$s \sim t$ if and only if there exists $W \in I$ such that $W \subseteq U \cap V$ and $s \restriction W = t \restriction W$. One checks that $\sim$ is an equivalence relation. \\
	Now, we consider the quotient of the disjoint union of the $\mathscr{F}(U)$'s.
	\[
	\varinjlim \mathscr{F}(U) \coloneqq \coprod_{U \in I} \mathscr{F}(U) \bigg/ \sim 
	\]
	Note that for any two elements $U, V \in I$, one has $[0_U] = [0_V]$ and $[1_U] = [1_V]$, where $[0_U]$ (\textit{resp.} $[1_U]$) denotes the class of the zero element (\textit{resp.} the multiplicative unit) of the ring $\mathscr{F}(U)$. \\
	Last, on each component $\mathscr{F}(U)$ the ring operations of $\varinjlim \mathscr{F}(U)$ are those of $\mathscr{F}(U)$. 
\end{construction}

\begin{ex}
	Prove $(\varinjlim \mathscr{F}(U), 0, +, 1, \times)$ is a ring. 
\end{ex}

\begin{definition}[direct limit]
	Let $X$ be a topological space, $\mathscr{F}$ a sheaf of rings on $X$ and $I$ a set of open subsets of $X$. The direct limit over $I$ is the ring $\varinjlim \mathscr{F}(U)$.
\end{definition}

\begin{definition}[stalks of a presheaf]
	Let $X$ be a topological space, $\mathscr{F}$ a sheaf of rings on $X$ and $x$ an element of $X$. \\
	The stalk $\mathscr{F}_x$ of $\mathscr{F}$ at $x$ is the direct limit over the set of all the open neighborhoods of $x$.   
\end{definition}

\begin{definition}[locally ringed space]
	A locally ringed space is a ringed space $(X, \mathscr{O}_X)$ such that the stalk $(\mathscr{O}_X)_x$ is a local ring for every $x \in X$.
\end{definition}

@@

\begin{definition}[scheme]
	A scheme is a locally ringed space $(X, \mathscr{O}_X)$ in which every point has an open neighborhood $U$ such that the topological space $U$, together with the sheaf $\mathscr{O}_X | _U$, is an affine scheme.
\end{definition}
